---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ayu

<!-- badges: start -->
<!-- badges: end -->

The goal of `ayu` is to provide a suite of tools to standardise the look of visualisations. By using the beautiful palette of [ayu](https://github.com/ayu-theme/ayu-colors) colours.

## Installation

You can install the development version of ayu from [GitHub](https://github.com/aljrico/ayu) with:

```{r setup, eval  = FALSE}
# install.packages("devtools")
devtools::install_github("aljrico/ayu")
library(ayu)
```

```{r setup2, echo  = FALSE, eval = TRUE}
devtools::load_all()
```

## How to use

##### Main Colours

The most basic functionality `ayu` provides is the curated list of main colours. Simply retrieve them with:

```{r example}
get_main_colours()
```

##### Display Palette

A quick way to visualise and print the colours is to make use of the `display_palette()` function. This will simply print the list of colours it gets passed.

```{r display_palette, out.width="50%", fig.align = 'center'}
colours <- get_main_colours()
display_palette(
  c(
    colours$mirage$red,
    colours$mirage$yellow,
    colours$mirage$green,
    colours$mirage$blue
  ),
  xlab = 'Main Colours'
)
```

##### Sequential Palettes

A common approach to create palettes is to pick a main *hue* and modify the *saturation* and *value*. `ayu` provides a quick function to facilitate that while maintaining a cohesive feel.

```{r continuous_palettes_1, out.height='250px', dpi=500}
par(mfrow=c(1,2))
generate_sequential_palette(colours$mirage$red) |> display_palette()
generate_sequential_palette(colours$mirage$blue) |> display_palette()
```

The `generate_sequential_palette()` function also provides a `contrast` parameter to tweak the steepness of the gradient. 

```{r, out.height='250px', dpi=500}
par(mfrow=c(1,2))
generate_sequential_palette(colours$mirage$orange, contrast = 0.3) |> display_palette()
generate_sequential_palette(colours$mirage$orange, contrast = 0.6) |> display_palette()
```

And the `n` parameter to select the number of colours generated

```{r, out.height='250px', dpi=500}
par(mfrow=c(1,2))
generate_sequential_palette(colours$mirage$purple, n = 3) |> display_palette()
generate_sequential_palette(colours$mirage$purple, n = 15) |> display_palette()
```

##### Expand Palette

To facilitate custom design of divergent palettes, the `ayu` package provides the `expand_palette()` function, that will take an arbitrary number of colours and create a continuum between them

```{r, out.height='250px', dpi=500}
par(mfrow=c(1,2))
expand_palette(c(colours$mirage$green, colours$mirage$red), n = 10) |> display_palette()
expand_palette(c(colours$mirage$green, colours$mirage$red), n = 100) |> display_palette()
```


##### Diverging Palettes


The package also contains a few predefined diverging palettes. Those are available as stand-alone functions.

```{r, fig.height=5}
par(mfrow=c(2,2))
diverging_palette('darkBlueYellow') |> display_palette(xlab = 'darkBlueYellow')
diverging_palette('yellowRed') |> display_palette(xlab = 'yellowRed')
diverging_palette('spectral') |> display_palette(xlab = 'spectral')
diverging_palette('myridis') |> display_palette(xlab = 'myridis')
```

