---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ayu

<!-- badges: start -->
<!-- badges: end -->

The goal of `ayu` is to provide a suite of tools to standardise the look of visualisations. By using the beautiful palette of [ayu](https://github.com/ayu-theme/ayu-colors) colours.

## Installation

You can install the development version of ayu from [GitHub](https://github.com/aljrico/ayu) with:

```{r setup}
# install.packages("devtools")
devtools::install_github("aljrico/ayu")
library(ayu)
```

## How to use

##### Main Colours

The most basic functionality `ayu` provides is the curated list of main colours. Simply retrieve them with:

```{r example}
get_main_colours()
```

##### Display Palette

A quick way to visualise and print the colours is to make use of the `display_palette()` function. This will simply print the list of colours it gets passed.

```{r display_palette, out.width="50%", fig.align = 'center'}
colours <- get_main_colours()
display_palette(
  c(
    colours$mirage$red,
    colours$mirage$yellow,
    colours$mirage$green,
    colours$mirage$blue
  ),
  xlab = 'Main Colours'
)
```

##### Continuous Palettes

A common approach to create palettes is to pick a main *hue* and modify the *saturation* and *value*. `ayu` provides a quick function to facilitate that while maintaining a cohesive feel.

```{r continuous_palettes_1, out.height='250px', dpi=500}
par(mfrow=c(1,2))
generate_continuous_palette(palettes$mirage$red) |> display_palette()
generate_continuous_palette(palettes$mirage$blue) |> display_palette()
```

The `generate_continuous_palette()` function also provides a `contrast` parameter to tweak the steepness of the gradient. 

```{r, out.height='250px', dpi=500}
par(mfrow=c(1,2))
generate_continuous_palette(palettes$mirage$orange, contrast = 0.3) |> display_palette()
generate_continuous_palette(palettes$mirage$orange, contrast = 0.6) |> display_palette()
```

And the `n` parameter to select the number of colours generated

```{r, out.height='250px', dpi=500}
par(mfrow=c(1,2))
generate_continuous_palette(palettes$mirage$purple, n = 3) |> display_palette()
generate_continuous_palette(palettes$mirage$purple, n = 15) |> display_palette()
```
