---
output: github_document
---



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![cran version](http://www.r-pkg.org/badges/version/ayu)](https://cran.r-project.org/package=ayu)
[![rstudio mirror per-month downloads](http://cranlogs.r-pkg.org/badges/ayu)](https://github.com/metacran/cranlogs.app)
[![rstudio mirror total downloads](http://cranlogs.r-pkg.org/badges/grand-total/ayu?color=yellowgreen)](https://github.com/metacran/cranlogs.app)



# ayu

<!-- badges: start -->
<!-- badges: end -->

This package provides a user-friendly API to add some of the beautiful Ayu colours into R plots.

## Installation

You can install the released version of ayu from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("ayu")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("aljrico/ayu")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example 1}
library(ayu)
pal <- ayu(n = 8, option = "sequential1")
image(volcano, col = pal)

pal <- ayu(n = 128, option = "sequential1")
image(volcano, col = pal)
```

## ggplot2

Of course, this package has specific functions to behave seamlessly with the best data visiualisation library available. 
The package contains colour scale functions for **ggplot2** plots: `scale_colour_ayu()` and `scale_fill_ayu()`. 


```{r example 2}
library(ggplot2)
ggplot(data.frame(x = rnorm(1e4), y = rnorm(1e4)), aes(x = x, y = y)) +
  geom_hex() + 
	coord_fixed() +
  scale_fill_ayu(option = "sequential3") + 
	theme_bw()
```

### Qualitative Scales

But what if you want discrete scales? These functions also can be used for discrete scales with the argument `discrete = TRUE`. This argument, when TRUE, sets a finite number of sufficiently spaced colours within the selected palette to plot your data.


```{r example 3}
ggplot(diamonds, aes(factor(color), fill=factor(cut))) +
	geom_bar(colour = "black") +
	scale_fill_ayu(discrete = TRUE, option = "qualitative1", name = "Cut", direction = -1) +
	ylab("") +
	xlab("Colour") +
	coord_flip()
```