---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ayu

<!-- badges: start -->
<!-- badges: end -->

The goal of `ayu` is to provide a suite of tools to standardise the look of visualisations. By using the beautiful palette of [ayu](https://github.com/ayu-theme/ayu-colors) colours.

## Installation

You can install the development version of ayu from [GitHub](https://github.com/aljrico/ayu) with:

```{r setup}
# install.packages("devtools")
devtools::install_github("aljrico/ayu")
library(ayu)
```

## How to use

##### Main Colours

The most basic functionality `ayu` provides is the curated list of main colours. Simply retrieve them with:

```{r example}
get_main_colours()
```

##### Display Palette

A quick way to visualise and print the colours is to make use of the `display_palette()` function. This will simply print the list of colours it gets passed.

```{r display_palette}
colours <- get_main_colours()
display_palette(
  c(
    colours$mirage$red,
    colours$mirage$yellow,
    colours$mirage$green,
    colours$mirage$blue
  ),
  xlab = 'Main Colours'
)
```

##### Continuous Palettes



```{r cars}
par(mfrow=c(2,3))
generate_continuous_palette(palettes$mirage$red) |> display_palette(xlab = 'Red')
generate_continuous_palette(palettes$mirage$blue) |> display_palette(xlab = 'Blue')
generate_continuous_palette(palettes$mirage$green) |> display_palette(xlab = 'Green')
generate_continuous_palette(palettes$mirage$orange) |> display_palette(xlab = 'Orange')
generate_continuous_palette(palettes$mirage$yellow) |> display_palette(xlab = 'Yellow')
generate_continuous_palette(palettes$mirage$purple) |> display_palette(xlab = 'Purple')
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
